An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-25 EconGrowthSeminar.Rnw
Changed a few limits to the CI vs. parameter graphs.

\begin{frame}{World Oil Supply is Tightening}{\citep{Tverberg:2013}} %----------------------------
  \includegraphics[width=4.0in]{figure_other/Figure_Tverberg_2013.png}
\end{frame}

@@

\minorSeparator{The Question\\ \normalsize      %----------------------------
\vspace{\baselineskip} 
Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?}

@@

\begin{frame}{CI and $\gamma$ in Cobb-Douglas} %----------------------------
<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
@
\end{frame}

@@

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
CIvsParamPlot(model="CES", param="delta", energyType="Q")
@
\end{frame}

@@

\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
CIvsParamPlot(model="CES", param="sigma", energyType="Q")
@
\end{frame}

@@

>>>>

\begin{frame}{World Oil Supply is Tightening}{\citep{Tverberg:2013b}} %----------------------------
  \includegraphics[width=4.0in]{figure_other/Figure_Tverberg_2013b.png}
\end{frame}

@@

\minorSeparator{The Question} %----------------------------

\begin{frame}{The Question} %----------------------------
  \begin{center}
    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?

    \pause

    No known studies of comparing economic growth models for various types of economies on a rigorous statistical basis.
  \end{center}
\end{frame}

@@

\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with Energy} %----------------------------
<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
@
\end{frame}

@@

\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES} %----------------------------
<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
CIvsParamPlot(model="CES", param="delta", energyType="Q")
@
\end{frame}

@@

\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES} %----------------------------
<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
CIvsParamPlot(model="CES", param="sigma", energyType="Q")
@
\end{frame}

@@

\minorSeparator{Introduction} %----------------------------

\begin{frame}{Energy Cost Share}{\citep{Tverberg:2013a}} %----------------------------
  \begin{center}
    \includegraphics[height=6.3cm]{figure_other/Figure_Tverberg_2013a.png}
  \end{center}
\end{frame}
